Action Groupoids and Fractional Types

### 2016-07-06 pibackground.tex
small changes in first sections

\paragraph{Intermezzo.} For an information-theoretic perspective on
the language $\Pi$, we think of a type containing $N$ values as an
abstract system that has~$N$ distinguishable states. According to the
conventional theory of information~\cite{Shannon1948}, the amount of
information contained in each state of a system with $N$
distinguishable states is $\log N$ bits of information. For example,
the type $\mathbb{2}$ can be thought of as an abstract system with
two distinguishable states labeled $\mathsf{true}$ and
$\mathsf{false}$ each containing $\log 2 = 1$ bit. Similarly, the type
$\mathbb{3}$ can be thought of as an abstract system with three
distinguishable states each containing $\log 3$ bits. The logarithmic
map implies that information contained in a composite state is the sum
of the information contained in its constituents. For example, the
type $\mathbb{2} \otimes \mathbb{3}$ can be thought of a composite
system consisting of two independent unrelated subsystems. Each state
of the composite system therefore contains
$\log (2 * 3) = \log 2 + \log 3$ bits which is the sum of the
information contained in each subsystem. Since all the combinators
preserve cardinality, they are also information-preserving.

>>>>

\paragraph{Intermezzo.} For an information-theoretic perspective on
the language $\Pi$, we think of a type containing $N$ values as an
abstract system that has~$N$ distinguishable states. According to the
conventional theory of information~\cite{Shannon1948}, the amount of
information contained in each state of a system with $N$
distinguishable states is $(\log N)$ bits of information. For example,
the type $\mathbb{2}$ can be thought of as an abstract system with
two distinguishable states labeled $\mathsf{true}$ and
$\mathsf{false}$ each containing $\log 2 = 1$ bit. Similarly, the type
$\mathbb{3}$ can be thought of as an abstract system with three
distinguishable states each containing $\log 3$ bits. The logarithmic
map implies that information contained in a composite state is the sum
of the information contained in its constituents. For example, the
type $\mathbb{2} \otimes \mathbb{3}$ can be thought of a composite
system consisting of two independent unrelated subsystems. Each state
of the composite system therefore contains
$\log (2 * 3) = \log 2 + \log 3$ bits which is the sum of the
information contained in each subsystem. Since all the combinators
preserve cardinality, they are also information-preserving.
